% Acknowledgments

\documentclass[main.tex]{subfiles}
\begin{document}

\chapter*{Acknowledgments}
{
\setlength{\parindent}{0cm}
\setlength{\parskip}{12pt}

First, I'd like to thank my academic advisor Prof. Osswald for your trust,  patience, and words of encouragement during my stay at the PEC. \emph{Quedo siempre en su deuda por haberme adoptado en su grupo}.

Thank you to Prof. Rudolph for being my advisor during my first year of grad school! Please know that your enthusiasm and tenacity were a constant source of inspiration through all my years of studies. 

My most sincere gratitude to the members of my committee: Prof. Turng, Prof. Prabhakar, Prof. Rold\'an, and Prof. Chen for your valuable input and time.

Thank you to the entire PEC family for creating a great environment to grow professionally and personally. I've learned a thing or two from all of you, and I can only hope that you learned from me as well. In particular, I'd like to thank Tom, Luke, Jos\'e, Alec, and Zijie for having the patience to work directly with me in a variety of different projects. You can now admit this was the hardest part of your PhD (or in the case of Zijie, the hardest part \emph{so far}).

Thank you to all of the undergrads and visiting scholars that provided aid in making all the moving parts of this project work! Special mentions go to Paul, Varun, Thibaut, Colby, Graydon, Apoorv, and Evan, whose contributions represent an integral part of this dissertation.

Thank you to all of the friends I met in Madison. In particular, I'd like to thank everyone that shared a roof with me (officially or unofficially) at one point or another, for being in many ways my family away from home. 

Finally, \emph{gracias a mi familia, a quienes les debo todo}. 

}
\end{document}